---
title: "Generate the Evening QC plots"
format: html
---

Specify a desired location

```{r}
StorageLocation <- file.path("Figures", "Figure_EveningQC")

Instrument <- "4L"
```

Read in the processed data for the respective instrument

# MFI

```{r}
Location <- paste0("data/EveningQCDrift", Instrument, "MFI.csv")
TheData <- read.csv(Location, check.names=FALSE)
```

And proceed to tidying the dataset for use in plotting

```{r}
TheData$Timepoint <- gsub("_NA", "", TheData$Timepoint)
colnames(TheData)

MFIStart <- tail(which(stringr::str_detect(colnames(TheData), "rCV")), 1) + 1
MFIEnd <- length(colnames(TheData))

GainStart <- head(which(stringr::str_detect(colnames(TheData), "Gain")), 1)
GainEnd <- head(which(stringr::str_detect(colnames(TheData), "aser")), 1)-1

RCVStart <- head(which(stringr::str_detect(colnames(TheData), "rCV")), 1)
RCVEnd <- tail(which(stringr::str_detect(colnames(TheData), "rCV")), 1)

Detectors <- colnames(TheData)[MFIStart:MFIEnd]

LongData <- TheData |>
  tidyr::pivot_longer(
    cols = all_of(MFIStart:MFIEnd),
    names_to = "Detectors",
    values_to = "MFI"
  )

DetectorIndex <- which(stringr::str_detect(colnames(LongData), "Detectors"))
MFIIndex <- which(stringr::str_detect(colnames(LongData), "MFI"))

PlottingData <- LongData[c(1:(GainStart-1), DetectorIndex, MFIIndex)]
PlottingData
```

Now we can prepare things for plotting 

```{r}
TheFactors <- PlottingData |> pull(Timepoint) |> unique() |> length()

if (TheFactors == 4){
    PlottingData$Timepoint <- factor(PlottingData$Timepoint, levels=c("Before", "After", "Before_Evening", "After_Evening"))
} else (stop("The factoring got messed up"))
```

Prepare our processing and plotting function

```{r}
FireTheCannon <- function(x, data){
    InternalData <- data |> filter(Detectors %in% x)
    plot <- ggplot(InternalData, aes(x = Timepoint, y = MFI, group = DATE, color = TimeDifference)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) + 
  labs(title=x) +
  theme_bw()
return(plot)
}
```

```{r}
PlottingData1 <- PlottingData |> filter(DATE != "2024-12-05") #Bead Lot Switch Date

ThePlots <- purrr::map(.x=Detectors, .f=FireTheCannon, data=PlottingData1)
ThePlots[[1]]
#plotly::ggplotly(ThePlots[[1]])

TheFileName <- paste0("EveningQCDrift", Instrument, "MFI")

Utility_Patchwork(x=ThePlots, filename = TheFileName, outfolder=StorageLocation,
thecolumns=1, therows=3, width=7, height=9, returntype="pdf", NotListofList = TRUE)
```

For individual plot returns

```{r}
#This
```

# RCV

```{r}
Location <- paste0("data/EveningQCDrift", Instrument, "RCV.csv")
TheData <- read.csv(Location, check.names=FALSE)
```

And proceed to tidying the dataset for use in plotting

```{r}
TheData$Timepoint <- gsub("_NA", "", TheData$Timepoint)
colnames(TheData)

RCVStart <- head(which(stringr::str_detect(colnames(TheData), "-A")), 1)
RCVEnd <- tail(which(stringr::str_detect(colnames(TheData), "-A")), 1)

Detectors <- colnames(TheData)[RCVStart:RCVEnd]

LongData <- TheData |>
  tidyr::pivot_longer(
    cols = all_of(RCVStart:RCVEnd),
    names_to = "Detectors",
    values_to = "RCV"
  )

DetectorIndex <- which(stringr::str_detect(colnames(LongData), "Detectors"))
RCVIndex <- which(stringr::str_detect(colnames(LongData), "RCV"))

PlottingData <- LongData #[c(1:(GainStart-1), DetectorIndex, RCVIndex)]
PlottingData
```

Now we can prepare things for plotting 

```{r}
TheFactors <- PlottingData |> pull(Timepoint) |> unique() |> length()

if (TheFactors == 4){
    PlottingData$Timepoint <- factor(PlottingData$Timepoint, levels=c("Before", "After", "Before_Evening", "After_Evening"))
} else (stop("The factoring got messed up"))
```

Prepare our processing and plotting function

```{r}
FireTheCannon <- function(x, data){
    InternalData <- data |> filter(Detectors %in% x)
    plot <- ggplot(InternalData, aes(x = Timepoint, y = RCV, group = DATE, color = TimeDifference)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  scale_y_continuous(labels = scales::percent) + 
  labs(title=x) +
  theme_bw()
return(plot)
}
```

```{r}
PlottingData1 <- PlottingData |> filter(DATE != "2024-12-05") #Bead Lot Switch Date

ThePlots <- purrr::map(.x=Detectors, .f=FireTheCannon, data=PlottingData1)
ThePlots[[1]]
#plotly::ggplotly(ThePlots[[1]])

TheFileName <- paste0("EveningQCDrift", Instrument, "RCV")

Utility_Patchwork(x=ThePlots, filename = TheFileName, outfolder=StorageLocation,
thecolumns=1, therows=3, width=7, height=9, returntype="pdf", NotListofList = TRUE)
```

For individual plot returns

```{r}
#This
```

# Conclusion

```{r}
print("Goodbye")
```


