---
title: "Instrument Usage"
format: html
---
Set storage location for the completed plots

```{r}
StorageLocation <- file.path("Figures", "Figure_InstrumentUsage")
```

First load required packages via the library call

```{r}
library(dplyr)
library(lubridate)
library(Luciernaga)
#library(stringr)
library(ggplot2)
```

Bring in the processed Application Log datasets from UMGCC FCSS InstrumentQC dashboard for each instrument of interest

```{r}
# Cytek Aurora 3L

CSV <- data_path <-                                                
    paste(                                                  
      "https://raw.githubusercontent.com",                  
      "UMGCCFCSS", "InstrumentQC",                   
      "main", "data", "3L", "Archive", "ApplicationData3L.csv",                              
      sep = "/"                                             
    ) 

TheList <- c("3L")

Data <- read.csv(CSV, check.names=FALSE)
Data$DateTime <- lubridate::ymd_hms(Data$DateTime)
Data3L <- Data |> mutate(Instrument = "3L")
```

```{r}
# Cytek Aurora 3L

CSV <- data_path <-                                                
    paste(                                                  
      "https://raw.githubusercontent.com",                  
      "UMGCCFCSS", "InstrumentQC",                   
      "main", "data", "4L", "Archive", "ApplicationData4L.csv",                              
      sep = "/"                                             
    ) 

TheList <- c("4L")

Data <- read.csv(CSV, check.names=FALSE)
Data$DateTime <- lubridate::ymd_hms(Data$DateTime)
Data4L <- Data |> mutate(Instrument = "4L")
```

```{r}
# Cytek Aurora 5L

CSV <- data_path <-                                                
    paste(                                                  
      "https://raw.githubusercontent.com",                  
      "UMGCCFCSS", "InstrumentQC",                   
      "main", "data", "5L", "Archive", "ApplicationData5L.csv",                              
      sep = "/"                                             
    ) 

TheList <- c("5L")

Data <- read.csv(CSV, check.names=FALSE)
Data$DateTime <- lubridate::ymd_hms(Data$DateTime)
Data5L <- Data |> mutate(Instrument = "5L")
```

```{r}
Data <- bind_rows(Data3L, Data4L, Data5L)
```

```{r}
Data$DateTime <- ymd_hms(Data$DateTime)

Data <- Data %>% mutate(Weekday = wday(DateTime, label = TRUE, abbr = FALSE),
                 Days_to_Sunday = (wday(DateTime) - 1) %% 7)

Data <- Data %>% mutate(PreviousSunday = DateTime - days(Days_to_Sunday)) %>%
    select(-Weekday, -Days_to_Sunday)
```

For the poster, filtering for the last two years of data, and excluding the really late/early timepoints that were mostly me running the bleach testing experiments on weekends. 

```{r}
RecentData <- Data |> filter(year(DateTime) >= 2024) |>
  filter(hour(DateTime) >= 8)  |> filter(hour(DateTime) <= 24) 
```

#### 3L

```{r}
#| echo: false
The3L <- Luciernaga:::UsagePlot(data=RecentData, TheInstrument="3L",
 returnType="ByFifteen", desiredfill = "royalblue", textsizey=6, textsizex=7)

filename <- "Cytek3LUsage.png"
TheFile <- file.path(StorageLocation, filename)

ggsave(filename = TheFile, The4L, dpi = 600, width = 4, height = 3)
```

```{r}
#| echo: false
plotly::ggplotly(The3L)
```

#### 4L

```{r}
#| echo: false
The4L <- Luciernaga:::UsagePlot(data=RecentData, TheInstrument="4L",
 returnType="ByFifteen", desiredfill = "royalblue", textsizey=6, textsizex=7)

filename <- "Cytek4LUsage.png"
TheFile <- file.path(StorageLocation, filename)

ggsave(filename = TheFile, The4L, dpi = 600, width = 4, height = 3)
```

```{r}
#| echo: false
plotly::ggplotly(The4L)
```

#### 5L

```{r}
#| echo: false
The5L <- Luciernaga:::UsagePlot(data=RecentData, TheInstrument="5L",
 returnType="ByFifteen", desiredfill = "royalblue", textsizey=6, textsizex=7)

filename <- "Cytek5LUsage.png"
TheFile <- file.path(StorageLocation, filename)

ggsave(filename = TheFile, The5L, dpi = 600, width = 4, height = 3)
```

```{r}
#| echo: false
plotly::ggplotly(The5L)
```

